Modeling site-specific amino-acid preferences deepens phylogenetic estimates of the divergence of viral proteins.

### 2018-03-08 manuscript/manuscript.tex
finished empirical trees paragraph

\skhcomment{I don't like how this paragraph comes almost as an afterthought from the next one given that branch lengths are actually are main point. I wonder if we can add a stronger first sentence to draw more emphasis to this paragraph. I also feel like a sentence between the current first and second one would be good. It could comment a bit more on the specifics of the results in Figure 4 in a way that draws out the point better.}
\ref{fig:empirical_trees} shows that modeling purifying selection via either $\Gamma\omega$ rate variation or a site-specific stationary state increases the estimated branch lengths.
But importantly, the effects from these two methods of modeling purifying selection are largely independent.
For every model (GY94 or any of the three ExpCM's), the $\Gamma\omega$ version estimates longer deep branches.
In addition, all ExpCM's estimate longer deep branches than the GY94 model, and all ExpCM+$\Gamma\omega$ models estimate longer deep branches than the GY94+$\Gamma\omega$ model.

>>>>

Models which account for purifying selection via either $\Gamma\omega$ rate variation or a site-specific stationary state are not just better fit models, they also increase the estimation of branch length on the HA tree. 
As \ref{fig:empirical_trees} shows, the tree optimized by without $\Gamma\omega$ rate variation and without a site-specific stationary state, the GY94 model, estimated the shortest branches of all eight models. 
Specifically, the ExpCM's defined by H1 HA or H3 HA amino-acid preferences estimated a tree which overall length is $\sim 8\%$ longer than the GY94 tree and the GY94+$\Gamma\omega$ model estimated tree which is $\sim 36\%$ longer than the GY94 tree. 
But importantly, the effects from these two methods of modeling purifying selection are largely independent.
For every model (GY94 or any of the three ExpCM's), the $\Gamma\omega$ version estimates longer deep branches.
In addition, all ExpCM's estimate longer deep branches than the GY94 model, and all ExpCM+$\Gamma\omega$ models estimate longer deep branches than the GY94+$\Gamma\omega$ model.
